A National Pipeline System as a Solution to Future Water Shortage in the United States

### 2013-02-04 paper.tex
dollar sign
added future research

\title{National Pipeline System as a Solution to Future Water Shortage in the United States}

@@

In light of the 2012-2013 drought season, and the larger problem of growing demand for water across the nation, 
our department has conducted an
analysis of how best to satisfy the water needs of the United States.

@@

@@

The cost of the proposed infrastructure developments are significant, at a total of $171 billion,
but must be placed in context. The cost of the 2012-2013 drought season
on the United States economy is estimated at between \$75 billion
and \$150 billion, and the potential total cost to the economy of
drought-related occurrences between 2013 and 2025 is much greater
even still.

>>>>

\title{A National Pipeline System as a Solution to Future Water Shortage in the United States}

@@

In light of the 2012-2013 drought season, and the larger problem of growing demand for water across the nation, 
our department has conducted an
analysis of how best to satisfy the growing water needs of the United States.

@@

\section{Avenues for Future Research}
A finer and more nuanced study of water usage and available data would provide a more complete model for water supplies and demands, as well as inform decisions about how to implement our proposals in reality. Here are some areas for future research:

\begin{itemize}
\item Groundwater level data is available in extreme detail from the US Geological Survey. Using this we can identify the areas of most severe exploitation as well as predict long-term aquifer lifespans. Areas with limited groundwater resources can then be prioritized in the building of the national pipelin network.
\item Research into currently available pipelines can be made if such data is collected; using these pipelines we predict that a large fraction of the network can simply be commandeered from existing infrastructure instead of built redundantly. This can be factored into the MST algorithm to give a minimal spanning tree based on pipelines already available. A problem with this approach is that available pipelines may not be of the condition or flow volume we require.
\item It is difficult with the granularity of the data available to actually model the optimal locations for specific de-salination plants and aqueducts to be built, although we can map out the general areas in which they are in need. The answer may perhaps be made on a case-by-case basis.
\item Reducing the total demand of the US is another approach that we did not address. New methods and technologies developed to this end should be used to inform our decisions about modeling the future demands of the US and decisions about pipeline-building.
\item Although we made the simplifying assumption that pipelines are the only largely available type of aqueduct, in reality in certain regions canals or other constructs may be more effective and less costly alternatives.
\end{itemize}

@@

The cost of the proposed infrastructure developments are significant, at a total of \$171 billion,
but must be placed in context. The cost of the 2012-2013 drought season
on the United States economy is estimated at between \$75 billion
and \$150 billion, and the potential total cost to the economy of
drought-related occurrences between 2013 and 2025 is much greater
even still.
